Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-20 tex/v3/appendix.tex
new appendix

\subsection{Proof of Lemma~\ref{lemma_actives_sets}}

@@

@@

\begin{figure*}[t]
	\centering

	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl10.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl1.pdf}
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl10.pdf}
	\caption{OT Domain Adaptation on a toy problem : running time gain for a toy dataset and for mnist as a function of the number of examples and the data decimation factor in \emph{Screenkhorn}}.
	\label{fig:otda}
\end{figure*}

\begin{figure*}[t]
	\centering
	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl1.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_accur_mnist_regcl10.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl1.pdf}
	\includegraphics[width=6.5cm]{../../figure/da_time_mnist_regcl10.pdf}
	\caption{OT Domain adaptation MNIST to USPS : (top) Accuracy and (bottom) running time of Sinkhorn and \emph{Screenkhorn} for hyperparameter of the $\ell_{p,1}$ regularizer (left) $\lambda = 1$ and (right) $\lambda=10$. Note that this
	value impact of the ground cost of each Sinkhorn problem involved in the iterative algorithm. The accuracy panels
	also report the performance of a $1$-NN when no-adaptation is performed.  
	We remark that the strenght of the class-based has influence on the performance of \emph{Screenkhorn} given a decimation factor. For small value on the left, Screenkhorn slightly performs better than Sinkhorn, while for large value, some
	decimation factors leads to loss of performances.
	Regarding, running time, we can note that Sinkhorn is far less efficient than
	\emph{Screenkhorn}  with an order of magnitude for intermediate number of samples.
	\label{fig:otda:mnist:extra}}
\end{figure*}

>>>>

%!TEX root = main.tex
\subsection{Proof of Lemma~\ref{lemma_actives_sets}}

@@

\subsection{Bounding dual objective values}

For each vectors $u \in \mathcal{U}_{\text{sc}}$ and $v\in \mathcal{V}_{\text{sc}}$ we define its rearrgement 
\begin{equation*}
\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top = (u_{I_{\varepsilon,\kappa}}^\top, \log(\frac\varepsilon\kappa)\mathbf1_{n- n_b}^\top)^\top,
\end{equation*}
and 
\begin{equation*}
\dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top = (v_{J_{\varepsilon,\kappa}}^\top, \log(\varepsilon\kappa)\mathbf 1_{m- m_b}^\top)^\top.
\end{equation*}

\begin{proposition}
Let $k\geq 1$ and $u^{sc}_k, v^{sc}_k$ be generated by Screenkhorn. Then, ones has 
\begin{align*}
\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
&\leq \norm{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
\end{align*}

\begin{align*}
\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
&\leq \norm{\kappa {u}^{\text{sc}}_k - {u}^\star}_\infty \norm{\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)\mathbf 1_m - {\mu}}_1 + \norm{\kappa^{-1}{v}^{\text{sc}}_k - {v}^\star}_\infty \norm{\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
&\qquad + (1- \kappa)\inr{{u}^{\text{sc}}_k ,\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{{v}^{\text{sc}}_k ,\tilde{B}({u}^{\text{sc}}_k ,{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
\end{align*}

\newpage
\begin{align*}
\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
&\leq \norm{\kappa {u}^{\text{sc}}_k - {u}^\star}_\infty \norm{\mu ^{\text{sc}}_k- {\mu}}_1 + \norm{\kappa^{-1}{v}^{\text{sc}}_k - {v}^\star}_\infty \norm{\nu^{\text{sc}}_k - {\nu}}_1\\
&\qquad + (1- \kappa)\inr{{u}^{\text{sc}}_k ,\mu ^{\text{sc}}_k} + (1- \kappa^{-1})\inr{{v}^{\text{sc}}_k ,\nu ^{\text{sc}}_k}.
\end{align*}

\end{proposition}

\newpage
\begin{proof}

Let $k\geq 0$ and $u^{sc}_k, v^{sc}_k$ be generated by Algorithm~\ref{screenkhorn} and $(u^\star, v^\star)$ be a solution of~\ref{sinkhorn-dual}. Then 
\begin{align*}
&\Psi_{\varepsilon, \kappa}(u^{sc}_k,v^{sc}_k) - \Psi(u^\star, v^\star)\\
& = \mathbf1_{n_b}^\top B(u_{I_{\varepsilon,\kappa}}, v_{J_{\varepsilon,\kappa}}) \mathbf 1_{m_b} + \varepsilon \kappa (e^{u_{I_{\varepsilon,\kappa}}})^\top K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})} + \varepsilon \kappa^{-1} K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}e^{v_{J_{\varepsilon,\kappa}}}\\
&\qquad - \kappa \mu_{I_{\varepsilon,\kappa}}^\top u_{I_{\varepsilon,\kappa}} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}^\top v_{J_{\varepsilon,\kappa}} + \Xi
\end{align*}

% \begin{proof}
Let us define $\tilde{K}$ a rearrgement of $K$ with respect to the active sets $I_{\varepsilon,\kappa}$ and $J_{\varepsilon,\kappa}$as follows:
\begin{equation*}
\tilde{K} = 
\begin{bmatrix}
K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &K_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
\end{bmatrix}.
\end{equation*}
For each vectors $u \in \mathcal{U}_{\text{sc}}$ and $v\in \mathcal{V}_{\text{sc}}$ we define its rearrgement 
\begin{equation*}
\dt{u} =(u_{I_{\varepsilon,\kappa}}^\top, u_{I^\complement_{\varepsilon,\kappa}}^\top)^\top = (u_{I_{\varepsilon,\kappa}}^\top, \log(\frac\varepsilon\kappa)\mathbf1_{n- n_b}^\top)^\top,
\end{equation*}
and 
\begin{equation*}
\dt{v} =(v_{J_{\varepsilon,\kappa}}^\top, v_{J^\complement_{\varepsilon,\kappa}}^\top)^\top = (v_{J_{\varepsilon,\kappa}}^\top, \log(\varepsilon\kappa)\mathbf 1_{m- m_b}^\top)^\top.
\end{equation*}
We then have 
\begin{equation*}
\Psi_{\varepsilon, \kappa} (u,v) = \mathbf 1_n^\top \tilde{B}(\dt{u}, \dt{v}) \mathbf 1_m - \kappa \dt{\mu}^\top \dt{u} - \kappa^{-1} \dt{\nu}^\top \dt{v},
\end{equation*}
where
\begin{equation*}
  \tilde{B}(\dt{u}, \dt{v}) = \Delta(e^{\dt{u}})\tilde{K} \Delta(e^{\dt{v}}).
\end{equation*}

Let us fix $k\geq 1$ and consider the convex function
	(\hat u, \hat v) \mapsto \inr{\mathbf 1_n, \tilde{B}(\dt{\hat u}^{\text{}} ,\dt{\hat v}^{\text{}})\mathbf 1_m} - \inr{\kappa\dt{\hat u}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{\hat v}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
Gradient inequality of any convex function g at point $x_o$ reads as $g(x_o) \geq g(x) + \inr{\nabla g(x), x_o - x}, \text{ for all } x \in \textbf{dom}(g).$
Applying the latter fact to the above function at point ($u^{\star}, v^{\star})$ we obtain
&\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
& - \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
& \leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
Moreover,
\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)
&= \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa\dt{u}^{\text{sc}}_k, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} - \inr{\kappa^{-1}\dt{v}_k^{\text{sc}}, \tilde{B}(\dt{u}_k^{\text{sc}}, \dt{v}^{\text{sc}}_k)\mathbf 1_n^\top}\\
& - \big( 
\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
&+ \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}.
Hence,
&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
&\qquad + \big( \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)\\
& \qquad -\inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} -\inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
& \leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
&\qquad + \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)
Then,
&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
&\leq \inr{\dt{u}^{\text{sc}}_k - \dt{u}^\star, (1-\kappa) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
+ \inr{\dt{v}^{\text{sc}}_k - \dt{v}^\star, (1-\kappa^{-1}) \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}\\
&\qquad + \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\kappa\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\kappa^{-1}\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n} \big)
\\
&\qquad + \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} + \inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
&\qquad - \big(\inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m}  
- \inr{\dt{u}^{\star{}}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} 
- \inr{\dt{v}^\star, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top \mathbf 1_n} \big).
So
&\Psi_{\varepsilon, \kappa} (u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
&\leq  \inr{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}} +\inr{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^{\star}, \tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
Applying Holder's inequality entails
&\Psi_{\varepsilon, \kappa}(u^{\text{sc}}_k ,v^{\text{sc}}_k) -\Psi(u^\star, v^\star)\\
&\leq \norm{\kappa \dt{u}^{\text{sc}}_k - \dt{u}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m - \dt{\mu}}_1 + \norm{\kappa^{-1}\dt{v}^{\text{sc}}_k - \dt{v}^\star}_\infty \norm{\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n - \dt{\nu}}_1\\
&\qquad + (1- \kappa)\inr{\dt{u}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)\mathbf 1_m} + (1- \kappa^{-1})\inr{\dt{v}^{\text{sc}}_k ,\tilde{B}(\dt{u}^{\text{sc}}_k ,\dt{v}^{\text{sc}}_k)^\top\mathbf 1_n}.
Next, we bound the right-hand side of this inequality.

If $r \in I^\complement_{\varepsilon, \kappa}$ then 
\begin{align*}
|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg| \log(\frac \varepsilon\kappa) - \log(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}})\bigg|\\
&= \bigg|\log\Big(\frac{\frac \varepsilon\kappa}{\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}}\Big) \bigg|\\
&= \bigg|\log\bigg(\frac{\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m \frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
& \leq \bigg|\log\bigg(\max_{1\leq j \leq m} \frac{K_{rj}e^{v^\star_j}}{\frac{\kappa \mu_r}{m\varepsilon}}\bigg) \bigg|\\
& \leq \big|\max_{1\leq j \leq m} (v_j^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})\big|\\
& \leq \norm{v^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
& \leq \norm{v^\star - v^{\text{sc}}_k - \log(\frac{\mu_r}{m\varepsilon^2})}_\infty \\
& \leq \norm{v^\star - v^{\text{sc}}_k}_\infty +  \log(m\varepsilon^2).
\end{align*}

If $r \in I_{\varepsilon, \kappa}$ then 
\begin{align*}
|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j\in J_{\varepsilon,\kappa}}K_{rj}e^{(v^{\text{sc}}_k)_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{rj}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
&= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
&= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
& \leq \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
& \leq \norm{(v^{\text{sc}}_k) - v^\star - \log(\kappa)}_\infty\\
& \leq \norm{(v^{\text{sc}}_k) - v^\star}_\infty (\kappa \leq 1)
\end{align*}

If $s \in J^\complement_{\varepsilon, \kappa}$ then 
\begin{align*}
|(\dt{v}^{\text{sc}}_k)_{s} - \dt{v}^\star_s| &= \bigg| \log(\varepsilon\kappa) - \log(\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}})\bigg|\\
&= \bigg|\log\Big(\frac{\varepsilon\kappa}{\frac{\nu_s}{\sum_{i=1}^n K_{is}e^{u^\star_i}}}\Big) \bigg|\\
&= \bigg|\log\bigg(\frac{\sum_{j=1}^n K_{is}e^{u^\star_i}}{\sum_{i=1}^n \frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
& \leq \bigg|\log\bigg(\max_{1\leq i \leq n} \frac{K_{is}e^{u^\star_i}}{\frac{\nu_s}{n\kappa\varepsilon}}\bigg) \bigg|\\
& \leq \big|\max_{1\leq i \leq n} (u_i^\star - \log(\frac{\nu_s}{n\kappa\varepsilon})\big|\\
& \leq \norm{u^\star - \log(\frac{\kappa \mu_r}{m\varepsilon})}_\infty \\
& \leq \norm{u^\star - u^{\text{sc}}_k - \log(\frac{\nu_s}{n\varepsilon^2})}_\infty \\
& \leq \norm{u^\star - u^{\text{sc}}_k}_\infty +  \log(n\varepsilon^2).
\end{align*}

If $r \in I_{\varepsilon, \kappa}$ then 
\begin{align*}
|(\dt{u}^{\text{sc}}_k)_{r} - \dt{u}^\star_r| &= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j\in J_{\varepsilon,\kappa}}K_{rj}e^{(v^{\text{sc}}_k)_j} + \varepsilon\kappa \sum_{j\in J^\complement_{\varepsilon,\kappa}}K_{rj}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
&= \bigg|\log\bigg(\frac{\kappa\mu_r}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg) - \log\bigg(\frac{\mu_r}{\sum_{j=1}^m K_{rj}e^{v^\star_j}}\bigg)\bigg|\\
&= \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
& \leq \bigg|\log\bigg(\frac{\kappa\sum_{j=1}^m K_{rj}e^{v^\star_j}}{\sum_{j=1}^m K_{rj}e^{(v^{\text{sc}}_k)_j}}\bigg)\bigg|\\
& \leq \norm{(v^{\text{sc}}_k) - v^\star - \log(\kappa)}_\infty\\
& \leq \norm{(v^{\text{sc}}_k) - v^\star}_\infty (\kappa \leq 1)
\end{align*}

\newpage
\begin{align*} 
\nabla_u \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) &= e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} \odot K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} + \varepsilon\kappa e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} \odot K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})} \mathbf 1_{m_b} - \kappa \mu_{I_{\varepsilon,\kappa}}\\
&= 
\begin{bmatrix}
e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}}\\
e^{u^{\text{sc}}_{I^\complement_{\varepsilon,\kappa}}}
\end{bmatrix}
\tilde{K}^1_O
\begin{bmatrix}
e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}}\\
e^{v^{\text{sc}}_{J^\complement_{\varepsilon,\kappa}}}
\end{bmatrix}
- \kappa \mu_{I_{\varepsilon,\kappa}},\\
\end{align*}
where 
\begin{equation*}
\tilde{K}^1_O = 
\begin{bmatrix}
K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} & K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
\end{bmatrix}.
\end{equation*}
and 
\begin{align*} 
\nabla_v \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) &= e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} \odot K^\top_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}} + \frac\varepsilon\kappa e^{v^{\text{sc}}_{J_{\varepsilon,\kappa}}} \odot K^\top_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} \mathbf 1_{n_b} - \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}\\
&= 
\begin{bmatrix}
e^{v^{\text{sc}}_{J_{\varepsilon, \kappa}}}\\
e^{v^{\text{sc}}_{J^\complement_{\varepsilon, \kappa}}}
\end{bmatrix}
\tilde{K}^2_O
\begin{bmatrix}
e^{u^{\text{sc}}_{I_{\varepsilon,\kappa}}}\\
e^{u^{\text{sc}}_{I^\complement_{\varepsilon,\kappa}}}
\end{bmatrix}
- \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}\\
\end{align*}
where 
\begin{equation*}
\tilde{K}^2_O = 
\begin{bmatrix}
K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}\\
K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})} &\mathbf O_{(I^\complement_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})}
\end{bmatrix}.
\end{equation*}
Therefore, we obtain 
\begin{equation*}
\nabla_u \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) = \tilde{B}^1_O(\dt{u}^{\text{sc}},\dt{v}^{\text{sc}}) \mathbf 1_m - \kappa \mu_{I_{\varepsilon,\kappa}} \text{ and } \nabla_v \Psi_{\varepsilon, \kappa}(u^{\text{sc}},v^{\text{sc}}) = \tilde{B}^2_O(\dt{u}^{\text{sc}},\dt{v}^{\text{sc}})^\top \mathbf 1_n- \kappa^{-1} \nu_{J_{\varepsilon,\kappa}}
\end{equation*}

Analogously, one can define 
\begin{align*}
\Psi(u^\star, v^\star) = \mathbf{1}_n \tilde{B}(\dt{u}^\star, \dt{v}^\star) \mathbf{1}_m - \dt{\mu}^\top \dt{u}^\star - \dt{\nu}^\top \dt{v}^\star
\end{align*}
Hence,
\begin{align*} 
 \Psi_{\varepsilon, \kappa} (u^{\text{}} ,v^{\text{}}) -\Psi(u^\star, v^\star)
& = \inr{\mathbf 1_n, \tilde{B}(\dt{u}^{\text{}} ,\dt{v}^{\text{}})\mathbf 1_m} - \inr{\mathbf{1}_n, \tilde{B}(\dt{u}^{\star} ,\dt{v}^{\star})\mathbf 1_m} + \inr{\dt{u}^{\star} - \kappa \dt{u}^{\text{}}, \dt{\mu}} + \inr{\dt{v}^{\star} - \kappa^{-1}\dt{v}^{\text{}}, \dt{\nu}}.
\end{align*}
\end{proof}

@@
